NFC and burnout in teachers - A replication and extension study

### 2021-11-01 Manuscript/Manuscript.Rmd
added description of years spent teaching
added item translation of DRR items

### *Structural equation model*
All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
Model parameters were estimated using the maximum likelihood method with robust standard errors.
Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.

@@

Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
As it was not preregistered, this was an exploratory analysis.
Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
However, because of the positive association of years spent teaching and self control ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
Therefore, the total effect also increased slightly, compared to the first model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).

@@

  fit_explor1_plot <- semPaths(fit_explor1, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 19, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```

>>>>

### *Structural equation model*
All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by the recoded items 12, 26, and 27, and DRF by items 17, 22, and 24.
The items can be translated as follows: 4) "There is too much pressure on me.", 8) "There is often too much being demanded of us at work.", 9) "I often feel tired and weary because of my work.", 12) "I can realize my ideas here.", 17) "I take pleasure in my work.", 22) "Does your place of work give you the opportunity to do what you do best?", 24) "Does your place of work give you enough opportunities to use your skills?", 26) "Are you happy with your promotion prospects?", and 27) "Are you happy with your position when comparing it to your skills?".
Model parameters were estimated using the maximum likelihood method with robust standard errors.
Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.

@@

Grass et al. [-@Grass2018] controlled for age and a-level grade in their analysis, which we did not consider when preregistering this analysis.
Since grade was not assessed in this sample, and age was assessed as a categorical variable, we instead incorporated how many years each participant had spent teaching at the point of assessment.
We placed this variable as an independent variable influencing self control, as the latter was the only variable in the model that showed a partial correlation with years spent teaching.
As it was not preregistered, this was an exploratory analysis.
Again, the baseline model did not fit the data ($\chi$^2^(`r round(fityears_summ$FIT[["baseline.df"]], digits = 0)`, $N = $`r nrow(data)`) = `r round(fityears_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$), and the fit indices of $CFI = $`r round(fityears_summ$FIT[["cfi"]], digits = 2)`, $TLI = $`r round(fityears_summ$FIT[["tli"]], digits = 2)`, $SRMR = $`r round(fityears_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA = $`r format(round(fityears_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fityears_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fityears_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
The associations between NFC, self control, reappraisal, suppression, and reduced personal efficacy were almost identical to the model first model.
However, because of the positive association of years spent teaching and self control ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "y"], digits = 2)`, $p < .001$), the indirect path leading from NFC and years spent teaching via self control to reduced personal efficacy reached significance in this model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Indirect1"], digits = 3)`).
Therefore, the total effect also increased slightly, compared to the first model ($\beta = $`r round(fityears_summ$PE$std.all[fityears_summ$PE$label == "Total"], digits = 2)`, $p = $`r round(fityears_summ$PE$pvalue[fityears_summ$PE$label == "Total"], digits = 3)`).

@@

  fit_explor1_plot <- semPaths(fit_explor1, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","rpe","NFC","DTH","DTL","DRF","RPE"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 19, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit_explor1_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
